---
title: "Dejavu II - Join"
output: html_notebook
---

```{r,echo=F}
DROOT = "/data/dejavuii/full-verified"
source("helpers.R")
```


Previous step: Downloader
Next step: verify

The join on all chunks (original Shabbir's projects redownloaded, missing projects from ghtorrent and all NPM packages with github repos), i.e. total of `86` files and `198GB` of compressed data was joined using the following command (at commit `8c71537d4bacfccc801b2ff565009506858865f4`):

```
time ./dejavu join -d=/data/dejavuii/data downloader=/array/dejavu/raw_input_data_never_delete > errors.csv
...
KTHXBYE!
real    1238m28.525s
user    789m48.813s
sys     489m2.437s     
```
The joined dataset is `113GB` and comprises of:

```
Projects:                    3 542 601
Commits:                    65 713 424
Distinct hashes:           285 302 286
File changes:            2 192 453 749
File paths:                303 285 296
Commit authors:              2 257 179
```

Another thing to notice is that there was a lot of repeated projects in the three datasets. 

## Chunks Summary

```{r}
chunks =  read_delim("../data/join-summary.csv", delim=',', escape_double=FALSE, escape_backslash=TRUE, quote="\"")
```

```{r}
chunks$valid = as.numeric(chunks$valid)
chunks$existing = as.numeric(chunks$existing)
chunks$errors = as.numeric(chunks$errors)
chunks$empty = as.numeric(chunks$empty)
numChunks = nrow(chunks)
LOG("Total chunks", data = numChunks)
validProjects = sum(chunks$valid)
existingProjects = sum(chunks$existing)
errorProjects = sum(chunks$errors)
emptyProjects = sum(chunks$empty)
totalProjects = errorProjects + emptyProjects + existingProjects + validProjects
LOG("Total projects", d = totalProjects)
LOG("Error projects", d = errorProjects, pct = totalProjects)
LOG("Empty projects", d = emptyProjects, pct = totalProjects)
LOG("Existing projects", d = existingProjects, pct = totalProjects)
LOG("Valid projects", d = validProjects, pct = totalProjects)
```

In total, `5.3m` projects were downloaded. 

There was a non-zero number of errors, but for all practical purposes it is 0. These were mostly error values in the `timings.csv` file produced by the downloader in the npm package chunks, which I believe is due to some cornercases in detection of whether npm modules has a github repo or not. 

Interesting is the number of existing projects - looking at the data, they only start to show up when the additional data is loader, so either there was no checking for pre-existence, or the check was not working. 

In total we end up with 66% of valid and useful projects, ammounting to just over 3.5m projects. 

The table of summaries for inspection:

```{r}
DT::datatable(chunks)
```

# The Full output

Here is the full captured output for reference:

```
peta@prl1e:~/devel/dejavuii/build$ time ./dejavu join -d=/data/dejavuii/data downloader=/array/dejavu/raw_input_data_never_delete > errors.csv
OH HAI CAN I HAZ DEJAVU AGAINZ?
Loading translated hashes...
Loading translated paths...
Loading translated users...
Loading already completed projects...
Analyzing directory /array/dejavu/raw_input_data_never_delete
Analyzing file /array/dejavu/raw_input_data_never_delete/data_31.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_31.tar.gz into /tmp/tmp.yfAHugHCBH...
Analyzing the chunk...
Done:k1k
    0 error projects
    1929 empty projects
    0 existing projects
    48071 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_15.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_15.tar.gz into /tmp/tmp.319HecdORD...
Analyzing the chunk...
Done:kk
    0 error projects
    1864 empty projects
    0 existing projects
    48136 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_29.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_29.tar.gz into /tmp/tmp.LFmGVVNxSj...
Analyzing the chunk...
Done:kkk
    0 error projects
    1730 empty projects
    0 existing projects
    48270 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_51.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_51.tar.gz into /tmp/tmp.74fKVeRl07...
Analyzing the chunk...
Done:kkk
    0 error projects
    909 empty projects
    0 existing projects
    24091 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_21.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_21.tar.gz into /tmp/tmp.yXYmqebD7u...
Analyzing the chunk...
Done:kkk
    0 error projects
    1817 empty projects
    0 existing projects
    48183 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_25.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_25.tar.gz into /tmp/tmp.Q04L3yP54M...
Analyzing the chunk...
Done:kkk
    0 error projects
    1813 empty projects
    0 existing projects
    48187 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_18.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_18.tar.gz into /tmp/tmp.JaYzlLTTq7...
Analyzing the chunk...
Done:kkk
    0 error projects
    1896 empty projects
    0 existing projects
    48104 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N21.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N21.tar.gz into /tmp/tmp.NBlJFPfVYh...
Analyzing the chunk...
Done:0kk
    0 error projects
    25421 empty projects
    5431 existing projects
    69148 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_23.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_23.tar.gz into /tmp/tmp.HEugdUWerI...
Analyzing the chunk...
Done:kkk
    0 error projects
    1908 empty projects
    709 existing projects
    47383 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_34.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_34.tar.gz into /tmp/tmp.va2TuS6ywC...
Analyzing the chunk...
Done:kkk
    0 error projects
    1853 empty projects
    774 existing projects
    47373 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_NPM05.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_NPM05.tar.gz into /tmp/tmp.TU1puuafgs...
Analyzing the chunk...
Error in mmalecki/nibbler-runner-local: No master commit available - likely no branches in the project
Error in sails/user: Unable to openfile /tmp/tmp.TU1puuafgs/commit_metadata/sai/sails_user.csv
Error in darthapo/1: Unable to openfile /tmp/tmp.TU1puuafgs/commit_metadata/dar/darthapo_1.csv
Error in node-prom-pushgateway/: Empty user or repo
Error in Jonathan/Rowell: Unable to openfile /tmp/tmp.TU1puuafgs/commit_metadata/Jon/Jonathan_Rowell.csv
Done:kkk
    5 error projects
    9800 empty projects
    1354 existing projects
    33665 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_45.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_45.tar.gz into /tmp/tmp.9bo0dT1R3U...
Analyzing the chunk...
Done:kk
    0 error projects
    1843 empty projects
    866 existing projects
    47291 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_09.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_09.tar.gz into /tmp/tmp.pupnTfXLg7...
Analyzing the chunk...
Error in frederikweber/FormGenerator: Empty author or commit time
Done:kkk
    1 error projects
    1859 empty projects
    851 existing projects
    47289 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_12.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_12.tar.gz into /tmp/tmp.HCGytib7Yu...
Analyzing the chunk...
Done:kk
    0 error projects
    1938 empty projects
    887 existing projects
    47175 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_14.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_14.tar.gz into /tmp/tmp.1hOOB0ETuz...
Analyzing the chunk...
Done:kkk
    0 error projects
    1836 empty projects
    826 existing projects
    47338 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_03.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_03.tar.gz into /tmp/tmp.VYFMUlbsiO...
Analyzing the chunk...
Done:kkk
    0 error projects
    880 empty projects
    422 existing projects
    23698 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N16.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N16.tar.gz into /tmp/tmp.jBeIjcLGUZ...
Analyzing the chunk...
Error in nuxodin/The.js: Empty author or commit time
Done:0kk
    1 error projects
    24786 empty projects
    10173 existing projects
    65040 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_11.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_11.tar.gz into /tmp/tmp.17QEwkD2PJ...
Analyzing the chunk...
Error in yatsyk/HNResources: Empty author or commit time
Done:kkk
    1 error projects
    1951 empty projects
    1499 existing projects
    46549 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N25.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N25.tar.gz into /tmp/tmp.vQVN6Alqfr...
Analyzing the chunk...
Done:0kk
    0 error projects
    25221 empty projects
    10902 existing projects
    63877 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_16.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_16.tar.gz into /tmp/tmp.0xgpg60oTr...
Analyzing the chunk...
Error in jgergic/gooddata.github.com: Empty author or commit time
Error in tedxuofw2018/1553396870424: Unable to openfile /tmp/tmp.0xgpg60oTr/commit_metadata/ted/tedxuofw2018_1553396870424.csv
Done:kk
    2 error projects
    1790 empty projects
    2285 existing projects
    45922 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_42.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_42.tar.gz into /tmp/tmp.gK8KolPhqp...
Analyzing the chunk...
Done:k2k
    0 error projects
    1805 empty projects
    2321 existing projects
    45874 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N11.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N11.tar.gz into /tmp/tmp.ihdzDWHXlY...
Analyzing the chunk...
Done:0kk
    0 error projects
    24363 empty projects
    12488 existing projects
    63149 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_10.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_10.tar.gz into /tmp/tmp.TVeCuDgoZC...
Analyzing the chunk...
Error in mxfli/OTA-test: Empty author or commit time
Done:kk
    1 error projects
    1885 empty projects
    2958 existing projects
    45156 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_41.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_41.tar.gz into /tmp/tmp.rI7xRpuanL...
Analyzing the chunk...
Done:kkk
    0 error projects
    1789 empty projects
    2952 existing projects
    45259 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N20.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N20.tar.gz into /tmp/tmp.WWe03EZhVp...
Analyzing the chunk...
Done:0kk
    0 error projects
    24846 empty projects
    14038 existing projects
    61116 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_49.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_49.tar.gz into /tmp/tmp.tmGmtymVun...
Analyzing the chunk...
Done:k0kk
    0 error projects
    940 empty projects
    1804 existing projects
    22256 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_08.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_08.tar.gz into /tmp/tmp.nt7Aa9mFnm...
Analyzing the chunk...
Done:kk
    0 error projects
    1882 empty projects
    3691 existing projects
    44427 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N05.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N05.tar.gz into /tmp/tmp.6PsEBO8Qw3...
Analyzing the chunk...
Done:0kk7k
    0 error projects
    24806 empty projects
    14906 existing projects
    60288 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_43.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_43.tar.gz into /tmp/tmp.5hblDf9nDe...
Analyzing the chunk...
Done:kk
    0 error projects
    1875 empty projects
    4423 existing projects
    43702 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_NPM01.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_NPM01.tar.gz into /tmp/tmp.zqx7kX6NTE...
Analyzing the chunk...
Error in Matt/Esch: Unable to openfile /tmp/tmp.zqx7kX6NTE/commit_metadata/Mat/Matt_Esch.csv
Error in kentcdodds/scope.macro: No master commit available - likely no branches in the project
Error in /: Empty user or repo
Error in /14717 : error when parsing inputs: Empty user or repo
Error in Vishal/Isharani: Unable to openfile /tmp/tmp.zqx7kX6NTE/commit_metadata/Vis/Vishal_Isharani.csv
Error in Yaniv/Keinan: Unable to openfile /tmp/tmp.zqx7kX6NTE/commit_metadata/Yan/Yaniv_Keinan.csv
Error in tlevine/r-pretty.barplot: No master commit available - likely no branches in the project
Error in alireza/alidoust: Unable to openfile /tmp/tmp.zqx7kX6NTE/commit_metadata/ali/alireza_alidoust.csv
Done:kk
    8 error projects
    10925 empty projects
    3995 existing projects
    35061 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_48.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_48.tar.gz into /tmp/tmp.zmgrT0qiJi...
Analyzing the chunk...
Done:kk
    0 error projects
    243 empty projects
    526 existing projects
    4911 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N01.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N01.tar.gz into /tmp/tmp.eLOstq073Q...
Analyzing the chunk...
Done:0kkk
    0 error projects
    24275 empty projects
    15638 existing projects
    60087 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_32.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_32.tar.gz into /tmp/tmp.RuBoMI8tG8...
Analyzing the chunk...
Done:kkk
    0 error projects
    1806 empty projects
    5135 existing projects
    43059 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N00.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N00.tar.gz into /tmp/tmp.QGvbQkupIo...
Analyzing the chunk...
Done:0k
    0 error projects
    24525 empty projects
    16291 existing projects
    59184 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_36.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_36.tar.gz into /tmp/tmp.PWkl2OVDpi...
Analyzing the chunk...
Done:kkk
    0 error projects
    1786 empty projects
    5933 existing projects
    42281 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N23.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N23.tar.gz into /tmp/tmp.g850wDMGwT...
Analyzing the chunk...
Done:0k
    0 error projects
    25177 empty projects
    17135 existing projects
    57688 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N04.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N04.tar.gz into /tmp/tmp.w4meElSOvb...
Analyzing the chunk...
Done:0kk
    0 error projects
    24336 empty projects
    17225 existing projects
    58439 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_33.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_33.tar.gz into /tmp/tmp.kceFTwFhuC...
Analyzing the chunk...
Done:kkk
    0 error projects
    1780 empty projects
    7201 existing projects
    41019 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_NPM03.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_NPM03.tar.gz into /tmp/tmp.RIyfdNQyEc...
Analyzing the chunk...
Error in neilstuartcraig/: Empty user or repo
Error in GuideSmiths/Ltd: Unable to openfile /tmp/tmp.RIyfdNQyEc/commit_metadata/Gui/GuideSmiths_Ltd.csv
Error in Your/name: Unable to openfile /tmp/tmp.RIyfdNQyEc/commit_metadata/You/Your_name.csv
Error in dotnsf/reverse_node: No master commit available - likely no branches in the project
Error in aux/awk: Unable to openfile /tmp/tmp.RIyfdNQyEc/commit_metadata/aux/aux_awk.csv
Error in Victor/Igor: Unable to openfile /tmp/tmp.RIyfdNQyEc/commit_metadata/Vic/Victor_Igor.csv
Error in /28962 : error when parsing inputs: Empty user or repo
Error in Gavin/Gong: Unable to openfile /tmp/tmp.RIyfdNQyEc/commit_metadata/Gav/Gavin_Gong.csv
Error in axdg/async: Unable to openfile /tmp/tmp.RIyfdNQyEc/commit_metadata/axd/axdg_async.csv
Error in /49353 : error when parsing inputs: Empty user or repo
Done:kk
    10 error projects
    10917 empty projects
    4924 existing projects
    34134 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N07.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N07.tar.gz into /tmp/tmp.t3c2vfnwAq...
Analyzing the chunk...
Done:0kk
    0 error projects
    24481 empty projects
    18017 existing projects
    57502 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_39.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_39.tar.gz into /tmp/tmp.cBlZ3RHHQF...
Analyzing the chunk...
Done:kkk
    0 error projects
    1830 empty projects
    8314 existing projects
    39856 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_02.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_02.tar.gz into /tmp/tmp.cOOWAWscll...
Analyzing the chunk...
Done:kkk
    0 error projects
    1869 empty projects
    8026 existing projects
    40105 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_50.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_50.tar.gz into /tmp/tmp.L2HJK1QJjU...
Analyzing the chunk...
Done:kkk
    0 error projects
    936 empty projects
    4011 existing projects
    20053 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_07.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_07.tar.gz into /tmp/tmp.xcK84Lp52q...
Analyzing the chunk...
Done:kkk
    0 error projects
    921 empty projects
    4051 existing projects
    20028 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_27.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_27.tar.gz into /tmp/tmp.5ZwqGJLjL6...
Analyzing the chunk...
Done:kkk
    0 error projects
    1820 empty projects
    8207 existing projects
    39973 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_28.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_28.tar.gz into /tmp/tmp.6ue53bdc7x...
Analyzing the chunk...
Error in storify/chrome: Empty author or commit time
Done:kk
    1 error projects
    1825 empty projects
    8128 existing projects
    40046 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_37.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_37.tar.gz into /tmp/tmp.TeOVK6doII...
Analyzing the chunk...
Error in SamWM/jQuery-Plugins: Empty author or commit time
Done:kk
    1 error projects
    1800 empty projects
    8294 existing projects
    39905 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_NPM02.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_NPM02.tar.gz into /tmp/tmp.APxyR9YNHq...
Analyzing the chunk...
Error in /: Empty user or repo
Error in node-google-custom-metrics/: Empty user or repo
Error in tlevine/r-markdown.list: No master commit available - likely no branches in the project
Error in /: Empty user or repo
Error in Tim/Kinnane: Unable to openfile /tmp/tmp.APxyR9YNHq/commit_metadata/Tim/Tim_Kinnane.csv
Done:kk
    5 error projects
    11023 empty projects
    5639 existing projects
    33326 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_01.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_01.tar.gz into /tmp/tmp.Z86sroIliY...
Analyzing the chunk...
Done:kkk
    0 error projects
    1791 empty projects
    8280 existing projects
    39929 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N24.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N24.tar.gz into /tmp/tmp.sH3gowY32h...
Analyzing the chunk...
Done:0kk
    0 error projects
    25487 empty projects
    22614 existing projects
    51898 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N26.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N26.tar.gz into /tmp/tmp.IZMLnpd55H...
Analyzing the chunk...
Done:0kk
    0 error projects
    25516 empty projects
    22986 existing projects
    51497 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_26.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_26.tar.gz into /tmp/tmp.RPL2zRaTdq...
Analyzing the chunk...
Done:kkk
    0 error projects
    1869 empty projects
    9613 existing projects
    38518 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N17.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N17.tar.gz into /tmp/tmp.WD1inSfM4z...
Analyzing the chunk...
Done:0k
    0 error projects
    25028 empty projects
    23492 existing projects
    51480 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_24.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_24.tar.gz into /tmp/tmp.Tvf0DlRoRD...
Analyzing the chunk...
Done:kkk
    0 error projects
    1856 empty projects
    10336 existing projects
    37808 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N22.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N22.tar.gz into /tmp/tmp.tBFLMqQxRB...
Analyzing the chunk...
Done:0kk
    0 error projects
    25188 empty projects
    24075 existing projects
    50737 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_38.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_38.tar.gz into /tmp/tmp.JRPRXnTmkl...
Analyzing the chunk...
Done:kk
    0 error projects
    1901 empty projects
    10818 existing projects
    37281 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_40.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_40.tar.gz into /tmp/tmp.qTtjgWSkXv...
Analyzing the chunk...
Error in JakSprats/node_AlchemyDatabase: Empty author or commit time
Done:kkk
    1 error projects
    1875 empty projects
    11018 existing projects
    37106 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N06.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N06.tar.gz into /tmp/tmp.nzioJLcYYs...
Analyzing the chunk...
Done:0k
    0 error projects
    24280 empty projects
    25660 existing projects
    50060 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N19.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N19.tar.gz into /tmp/tmp.I4L8R9BW5T...
Analyzing the chunk...
Done:0k
    0 error projects
    24620 empty projects
    25760 existing projects
    49620 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_35.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_35.tar.gz into /tmp/tmp.Hyw2JuSH1q...
Analyzing the chunk...
Done:kkk
    0 error projects
    1841 empty projects
    12450 existing projects
    35709 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_00.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_00.tar.gz into /tmp/tmp.KqrXmRoAcO...
Analyzing the chunk...
Done:kkk
    0 error projects
    1840 empty projects
    12231 existing projects
    35929 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_04.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_04.tar.gz into /tmp/tmp.B528mHkDE8...
Analyzing the chunk...
Done:kkk
    0 error projects
    1888 empty projects
    12353 existing projects
    35759 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N10.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N10.tar.gz into /tmp/tmp.nVE1OzgAdw...
Analyzing the chunk...
Done:0kk
    0 error projects
    24691 empty projects
    27900 existing projects
    47409 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N08.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N08.tar.gz into /tmp/tmp.ucSBkyPc7P...
Analyzing the chunk...
Done:0k5k
    0 error projects
    24458 empty projects
    27917 existing projects
    47625 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_22.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_22.tar.gz into /tmp/tmp.KCfpUiIswB...
Analyzing the chunk...
Done:kk
    0 error projects
    1848 empty projects
    13758 existing projects
    34394 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_13.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_13.tar.gz into /tmp/tmp.W8uWtpgRE1...
Analyzing the chunk...
Done:kkk
    0 error projects
    1823 empty projects
    13937 existing projects
    34240 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_30.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_30.tar.gz into /tmp/tmp.Bb5lfSubBw...
Analyzing the chunk...
Done:kkk
    0 error projects
    1818 empty projects
    13750 existing projects
    34432 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_47.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_47.tar.gz into /tmp/tmp.bGIgAzazWD...
Analyzing the chunk...
Done:kkk
    0 error projects
    1757 empty projects
    13609 existing projects
    34634 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_46.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_46.tar.gz into /tmp/tmp.dVd6s4dU6C...
Analyzing the chunk...
Done:kk
    0 error projects
    1804 empty projects
    13869 existing projects
    34327 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_52.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_52.tar.gz into /tmp/tmp.Vu17QbQbYi...
Analyzing the chunk...
Done:kkk
    0 error projects
    918 empty projects
    6829 existing projects
    17253 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N15.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N15.tar.gz into /tmp/tmp.HqtbZ7p9x7...
Analyzing the chunk...
Done:0k
    0 error projects
    24862 empty projects
    31292 existing projects
    43846 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N02.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N02.tar.gz into /tmp/tmp.SpHAyjSRrU...
Analyzing the chunk...
Done:0k
    0 error projects
    24040 empty projects
    31940 existing projects
    44020 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N27.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N27.tar.gz into /tmp/tmp.v0ajvHWXoH...
Analyzing the chunk...
Done:kk
    0 error projects
    17790 empty projects
    20624 existing projects
    27988 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_06.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_06.tar.gz into /tmp/tmp.j29JebpqkO...
Analyzing the chunk...
Done:kkk
    0 error projects
    1876 empty projects
    15462 existing projects
    32662 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_NPM00.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_NPM00.tar.gz into /tmp/tmp.Jun17HcMEV...
Analyzing the chunk...
Error in KrimZen/Ninja: Unable to openfile /tmp/tmp.Jun17HcMEV/commit_metadata/Kri/KrimZen_Ninja.csv
line 49991: Unterminated quote, starting at line 49991: iostream error
Done:
    1 error projects
    870 empty projects
    660 existing projects
    2482 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N14.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N14.tar.gz into /tmp/tmp.LPrz3fCBY2...
Analyzing the chunk...
Done:0k
    0 error projects
    24822 empty projects
    32237 existing projects
    42941 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N18.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N18.tar.gz into /tmp/tmp.sjtDMs2ufY...
Analyzing the chunk...
Error in bentruyman/enterprise-html: Empty author or commit time
Done:0k
    1 error projects
    24852 empty projects
    32290 existing projects
    42857 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_NPM04.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_NPM04.tar.gz into /tmp/tmp.LX2aUSRHyC...
Analyzing the chunk...
Error in node-simplespmacop/1562482038743: Unable to openfile /tmp/tmp.LX2aUSRHyC/commit_metadata/nod/node-simplespmacop_1562482038743.csv
Error in /25484 : error when parsing inputs: Empty user or repo
Error in samanime/xazure-utils: No master commit available - likely no branches in the project
Error in Syncplicity/Api: Unable to openfile /tmp/tmp.LX2aUSRHyC/commit_metadata/Syn/Syncplicity_Api.csv
Done:kk
    4 error projects
    10896 empty projects
    8112 existing projects
    30977 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_17.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_17.tar.gz into /tmp/tmp.kQhGTLnoDv...
Analyzing the chunk...
Done:kkk
    0 error projects
    1928 empty projects
    16972 existing projects
    31100 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_20.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_20.tar.gz into /tmp/tmp.h2qDbdu4bF...
Analyzing the chunk...
Done:kkk
    0 error projects
    1789 empty projects
    17006 existing projects
    31205 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N09.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N09.tar.gz into /tmp/tmp.xOlGGv6abp...
Analyzing the chunk...
Done:0kk
    0 error projects
    24913 empty projects
    33519 existing projects
    41568 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N12.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N12.tar.gz into /tmp/tmp.tiSOjd8Mg1...
Analyzing the chunk...
Done:0kk
    0 error projects
    24714 empty projects
    33792 existing projects
    41494 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_44.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_44.tar.gz into /tmp/tmp.qlzceYxtgm...
Analyzing the chunk...
Done:k5k
    0 error projects
    935 empty projects
    9236 existing projects
    14829 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_05.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_05.tar.gz into /tmp/tmp.rNpeK1aAUC...
Analyzing the chunk...
Done:kkk
    0 error projects
    1866 empty projects
    18612 existing projects
    29522 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_19.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_19.tar.gz into /tmp/tmp.aSR8CErPPP...
Analyzing the chunk...
Done:kk
    0 error projects
    979 empty projects
    9328 existing projects
    14693 valid projects
Analyzing file /array/dejavu/raw_input_data_never_delete/data_N13.tar.gz
Decompressing /array/dejavu/raw_input_data_never_delete/data_N13.tar.gz into /tmp/tmp.WYqdtlRja1...
Analyzing the chunk...
Done:0k
    0 error projects
    24843 empty projects
    35060 existing projects
    40097 valid projects
KTHXBYE!

real    1238m28.525s
user    789m48.813s
sys     489m2.437s
```